Are iPhone users more secure when using mobile enterprise systems?

### 2021-04-25 outputs/paper/paper.Rmd
update

The coefficient for **malicious_attack** is -0.303, suggesting that one unit increase in malicious_attack score is associated with 0.303 unit decrease in the perceived ES security, holding other variables constant.The p value is 0.000902, which indicates this is a significant result.

@@

\appendix

@@

```{r page1, echo=FALSE, fig.cap="Screen capture of the first part of the Survey.", out.width = '70%', fig.align="center"} 
knitr::include_graphics(here::here("outputs/paper/image/image1.png"))
```

## Appendix B 
The first 100 rows of raw data which will be used in regression is shown in the Table below. (Table \@ref(tab:rowdata))
```{r rowdata, echo=FALSE}
  head(clean_data,100)%>%
  kableExtra::kbl(caption = "First 100 rows Raw data ") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()
```
\newpage

>>>>

The coefficient for **malicious_attack** is 0. 219, suggesting that one unit increase in malicious_attack score is associated with 0.219 unit increase in the perceived ES security, holding other variables constant.The p value is 0.000902, which indicates this is a significant result.

@@

#appendix

@@

```{r page1, echo=FALSE, fig.cap="Screen capture of the survey invitation", out.width = '70%', fig.align="center"} 
knitr::include_graphics(here::here("outputs/paper/image/image1.png"))
```

```{r 1, echo=FALSE, fig.cap="Screen capture of the first part of the Survey.", out.width = '70%', fig.align="center"} 
knitr::include_graphics(here::here("outputs/paper/image/1.png"))
```

```{r 2, echo=FALSE, fig.cap="Screen capture of the second part of the Survey.", out.width = '70%', fig.align="center"} 
knitr::include_graphics(here::here("outputs/paper/image/2.png"))
```

```{r 3, echo=FALSE, fig.cap="Screen capture of the third part of the Survey.", out.width = '70%', fig.align="center"} 
knitr::include_graphics(here::here("outputs/paper/image/3.png"))
```

```{r 4, echo=FALSE, fig.cap="Screen capture of the fourth part of the Survey.", out.width = '70%', fig.align="center"} 
knitr::include_graphics(here::here("outputs/paper/image/4.png"))
```

```{r 5, echo=FALSE, fig.cap="Screen capture of the fifth part of the Survey.", out.width = '70%', fig.align="center"} 
knitr::include_graphics(here::here("outputs/paper/image/5.png"))
```

```{r 6, echo=FALSE, fig.cap="Screen capture of the sixth part of the Survey.", out.width = '70%', fig.align="center"} 
knitr::include_graphics(here::here("outputs/paper/image/6.png"))
```
## Appendix B 
The first 100 rows of raw data which will be used in regression is shown in the Table below. (Table \@ref(tab:rowdata))
```{r rowdata, echo=FALSE}
  head(clean_data,100)%>%
  kableExtra::kbl(caption = "First 100 rows Raw data ") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()
```
\newpage
